The Impact of Educational Expenses of New Coders

### 2021-04-21 outputs/paper/paper.Rmd
Edit model formulae

This equation \@ref(eq:linRegModel1) is a model formula for the regression model 1.

\begin{equation}
(\#eq:linRegModel1)
Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \epsilon
\end{equation}

This equation \@ref(eq:linRegModel2) is a model formula for the regression model 2.

\begin{equation}
(\#eq:linRegModel2)
Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \epsilon
\end{equation}

This equation \@ref(eq:linRegModel3) is a model formula for the regression model 3.

@@

>>>>

This equation \@ref(eq:linRegModel1) is a model formula for Model (1).

\begin{equation}
(\#eq:linRegModel1)
Y \sim \beta_0 + \beta_1X_1 + \epsilon
\end{equation}

This equation \@ref(eq:linRegModel2) is a model formula for Model (2).

\begin{equation}
(\#eq:linRegModel2)
Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \epsilon
\end{equation}

This equation \@ref(eq:linRegModel3) is a model formula for Model (3).

@@

This equation \@ref(eq:linRegModel4567) is a model formula for Model (4), (5), (6) and (7).

\begin{equation}
(\#eq:linRegModel4567)
Y \sim \beta_0 + \beta_1X_1 + \epsilon
\end{equation}
